Hypertension and microbiome

### 2019-05-02 articletwo.Rmd
Minor
Scatter plot

```{r libraries, cache = FALSE}
library(dplyr)
library(tibble)
library(phyloseq)
library(nortest)
library(microbiome)
library(finriskmetagcommon)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(ggpmisc)
library(Maaslin)
library(parallel)
library(officer)
library(flextable)
library(rvg)
library(tableone)
library(scales)
library(ggplot2)
library(gridExtra)
library(png)
library(pander)
library(ggpubr)
library(broom)
library(ggfortify)
```

@@

<details>
  <summary>Toggle imported core</summary>
### Officer functions

@@

@@

@@

</details>
# Loading data

@@

```{r alphabeta definitions}
dset.alpha <- meta.merge.alphadiversity(pseq.species)
alphadiversity <- list(
    min = calculateglm(dset.alpha, modelstring = "%s ~ BL_AGE + SEX  + diversities_shannon"),
    max = calculateglm(dset.alpha, modelstring = "%s ~ BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09 + diversities_shannon"))
diversities <- mergediversities(alphadiversity, adonis.species)
```

@@

```{r save grob}
alpha.diversity.min <- plot.alpha(diversities$min, colorlimit = 0.5)
alpha.diversity.max <- plot.alpha(diversities$max, colorlimit = 0.5)

@@

maas.all.pairs <- expand.grid(Feature = maas.results.df.signf %>% pull(Feature),
                         Name = maas.results.df.signf %>% pull(Name))
maas.tables.df <- merge(maas.results.df.signf,
                        maas.all.pairs,
                        all.y=TRUE,
                        by.y=c('Feature', 'Name'),
                        by.x=c('Feature', 'Name'))

maaslinplot <- ggplot(maas.tables.df, aes(x = Feature, y = reorder(Name, my.plot.order(Name)), fill = beta)) +
    geom_tile(aes(fill = 1)) +
    geom_tile(colour="white", size=0.25) +
    scale_fill_distiller(palette = "RdBu", name = "Effect size",
                         limits=c(-0.003, 0.003), breaks = c(-0.003, 0, 0.003), na.value="grey30") +
    coord_fixed() +
    xlab("") +
    ylab("") +
    theme_classic(10) +  
    theme(axis.text.x = element_text(angle = 90, hjust = 1.0, vjust=0.5, size=10),
          axis.text.y = element_text(size=10))

ggsave(file = "cache/maaslin.png", plot = maaslinplot, height = 3, width = 6, dpi = 300)
```

@@

>>>>

```{r libraries, cache = FALSE}
library(dplyr)
library(tibble)
library(phyloseq)
library(nortest)
library(microbiome)
library(finriskmetagcommon)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(ggpmisc)
library(Maaslin)
library(parallel)
library(officer)
library(flextable)
library(rvg)
library(tableone)
library(scales)
library(ggplot2)
library(gridExtra)
library(png)
library(pander)
library(ggpubr)
library(broom)
library(ggfortify)
library(RColorBrewer)
```

@@

### Officer functions

<details>
  <summary>Open/Close</summary>

@@

</details>

@@

<details>
  <summary>Open/Close</summary>

@@

</details>

# Loading data

@@

```{r alphabeta definitions}
dset.alpha <- meta.merge.alphadiversity(pseq.species) %>%
    mutate(diversities_shannon = scale(diversities_shannon),
           MAP = oMAP,
           PULSEPRESSURE = oPULSEPRESSURE,
           SYSTM = oSYSTM,
           DIASM = oDIASM)

alphadiversity <- list(
    min = calculateglm(dset.alpha,
                       modelstring = "%s ~ BL_AGE + SEX  + diversities_shannon"),
    max = calculateglm(dset.alpha,
                       modelstring = "%s ~ BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09 + diversities_shannon"))

diversities <- mergediversities(alphadiversity, adonis.species)
```

@@

```{r save grob}
alpha.diversity.min <- plot.alpha(diversities$min, colorlimit = 0.6)
alpha.diversity.max <- plot.alpha(diversities$max, colorlimit = 0.6)

@@

maas.all.pairs <- expand.grid(Feature = maas.results.df.signf %>% pull(Feature),
                         Name = maas.results.df.signf %>% pull(Name))
maas.tables.df <- merge(maas.results.df.signf,
                        maas.all.pairs,
                        all.y=TRUE,
                        by.y=c('Feature', 'Name'),
                        by.x=c('Feature', 'Name')) %>%
    mutate(p.groups = cut(P.value*ifelse(Coefficient < 0, -1, 1),
                          breaks = c(-0.05, -0.01, -0.001, 0, 0.001, 0.01, 0.05),
                          labels = c("beta < 0, p < 0.05",
                                     "beta < 0, p < 0.01",
                                     "beta < 0, p < 0.001",
                                     "beta > 0, p < 0.001",
                                     "beta > 0, p < 0.01",
                                     "beta > 0, p < 0.05")))

mycolors <- c("beta < 0, p < 0.05" = "#B2182B",
              "beta < 0, p < 0.01" = "#EF8A62",
              "beta < 0, p < 0.001" = "#FDDBC7",
              "beta > 0, p < 0.001" = "#D1E5F0",
              "beta > 0, p < 0.01" = "#67A9CF",
              "beta > 0, p < 0.05" = "#2166AC",
              "NA" = "gray50")

maaslinplot <- ggplot(maas.tables.df, aes(x = Feature,
                                          y = reorder(Name, my.plot.order(Name)),
                                          fill = p.groups)) +
    geom_tile(color = "white", aes(fill = "NA")) +
    geom_tile(color = "white") +
    scale_fill_manual(values = mycolors, name = "P-value", na.translate = F) +
    scale_x_discrete() +
    coord_fixed() +
    xlab("") +
    ylab("") +
    theme_classic(10) +  
    theme(axis.text.x = element_text(angle = 90, hjust = 1.0, vjust=0.5, size=10),
          axis.text.y = element_text(size=10))
ggsave(file = "cache/maaslin.png", plot = maaslinplot, height = 3, width = 6, dpi = 300)
```

@@

```{r scatter plots}
scatter.signf.bacteria <- paste0(maas.results.df.signf %>% pull(Feature) %>% unique %>% tolower, ".bacteria")

scatter.meta <- meta(pseq.genus) %>%
    tibble::rownames_to_column("id") %>%
      mutate(MAP = oMAP,
           PULSEPRESSURE = oPULSEPRESSURE,
           SYSTM = oSYSTM,
           DIASM = oDIASM) %>%
    gather("keym", "valuem", c(SYSTM, DIASM, MAP, PULSEPRESSURE))

scatter.abund <- abundances(pseq.genus, transform = "compositional") %>%
    t %>%
    as.data.frame %>%
    tibble::rownames_to_column("id") %>%
    setNames(tolower(replace.brackets(names(.)))) %>%
    select(id, scatter.signf.bacteria) %>%
    gather(key, value, -id) %>%
    mutate(value = asin(sqrt(value)))

scatter.full <- full_join(scatter.meta, scatter.abund, by = "id")

scatterplot <- ggplot(scatter.full, aes(y = valuem, x = value)) +
    facet_wrap(~key + keym, ncol=4, scales = "fixed") +
    geom_point(size=0.1, shape=1) +
    geom_smooth(method=lm, se=TRUE, size=0.5, color = 'Black') +
    stat_poly_eq(formula = "y ~ x",
                 aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
                 label.y =  -4,
                 parse = TRUE,
                 size = 2.5) +
    ylab("asin(sqrt(abundance))") +
    ggplot2::theme_minimal()

ggsave(file = "cache/scatter.png", plot = scatterplot, height = 20, width = 10, dpi = 300)
```
